---
title: "Lab 07 - Modelling course evaluations"
author: [TEAM NAME]
output: 
  tufte::tufte_html:
    css: ../lab.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse)
library(tidymodels)
library(patchwork)
```

### Read in data

```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```

### Exercise 1

```{r viz-score}
# add code here
evals %>%
  ggplot(aes(x=score)) +
  geom_histogram(binwidth = 0.1)
summarise(evals, av_score = mean(score), min_score = min(score), max_score = max(score))
```

The distribution of scores is definitely left skewed - we can also note that the mean score is 4.17 (3 s.f.) which is quite high - suggesting that students are scoring the professors quite generously. In addition, the fact that the minimum score rating is 2.3 is further evidence for this.

### Exercise 2

```{r viz-score-bty, eval = FALSE}
# add the code for each plot and assign them to the names as outlined below
# remove eval = FALSE from the code chunk options
# knit the document, and you'll see them appear next to each other
# this uses the patchwork package loaded above
# learn more about patchwork at https://patchwork.data-imaginist.com/
# it might be useful for your presentations!
plot_geom_point  <- ggplot(data=evals, aes(x=score, y=bty_avg)) +
  geom_point() +
  labs(x = "Score", y = "Average Beauty Rating of Professor")

plot_geom_jitter <- ggplot(data=evals, aes(x=score, y=bty_avg)) +
  geom_jitter() +
  labs(x = "Score", y = "Average Beauty Rating of Professor")

plot_geom_point + plot_geom_jitter
```

Jitter is adding a slight amount of random variation to each point - allowing us to see areas with high point density - this is something we can not see on the original plot as points being plotted on top of others are not distinguishable.

### Exercise 3

```{r fit-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(___ ~ ___, data = ___)
```

```{r tidy-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
tidy(___)
```

*Add your linear model here. Don't worry too much about notation, you can use things like score-hat.*

### Exercise 4

```{r viz-score_bty_fit}
# add your code here
```

### Exercise 5

*Add interpretation of intercept here.*

### Exercise 6

*Add interpretation of intercept here.*

### Exercise 7

```{r glance-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)
```

*Add interpretation of R-squared here.*

### Exercise 8

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___)
```

*Add your narrative here.*

### Exercise 9

```{r fit-score_rank_fit}
score_rank_fit <- evals %>%
  group_by(rank) %>%
  mutate(avg_score = mean(score)) 

score_rank_fit <- linear_reg() %>%
  set_engine("glm") %>%
  fit(avg_score ~ rank, data = score_rank_fit) %>%
  tidy()

score_rank_fit

```

The intercept indicates that score for professors based on rank are expected to be 4.28, on average.
The slope indicates that tenure track professor is expected to have higher score than tenured professor, on average

### Exercise 10

```{r fit-score_gender_fit}
score_gender_fit <- evals%>%
  group_by(gender) %>%
  mutate(avg_score = mean(score)) 

score_gender_fit <- linear_reg() %>%
  set_engine("glm") %>%
  fit(avg_score ~ gender, data = score_gender_fit) %>%
  tidy()
score_gender_fit
```

```{r score_gender_intercept, echo = FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- score_gender_fit %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
score_gender_intercept
```

```{r score_gender_slope, echo = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_gender_slope <-score_gender_fit %>% 
  filter(term == "gendermale") %>%
  select(estimate) %>%
  pull()
round(score_gender_slope, 10)
```

The intercept shows that score for female professors are expected to be 4.18, on average. 
The slope shows that male professors are expected to have higher score than female, on average.

### Exercise 11

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 12

```{r glance-score_bty_gender_fit}
# glance model output
```

*Add your narrative here.*

### Exercise 13

*Add your linear model here. Don't worry about math notation, you can use things like score-hat.*

### Exercise 14

*Add your narrative here. One sentence is sufficient.*

### Exercise 15

*Add your narrative here. One sentence is sufficient.*

### Exercise 16

*Add your narrative here. One sentence is sufficient.*

### Exercise 17

*Add your narrative here. One sentence is sufficient.*

### Exercise 18

```{r fit-score_bty_gender_rank_fit}
# fit model

# glance model output
```

*Add your narrative here. One sentence is sufficient.*
